Application of Micro-Rotors to Induce Crystal Nucleation: Challenges, Takeaways, and Future Prospects\\ PhD Thesis

### 2024-08-07 Latex_files/Thesis/chapters/chapter 4/main.tex
chp 4

For completeness the harmonic traps were located for dimers across a range 
of size ratios - from $a_{I}/a_{II} = 1$ to $a_{I}/a_{II}=10$ - while also 
recording the trap stiffness for each trap. The same simulation parameters are 
used here as for figures \ref{fig:paradigmatic} \& \ref{fig:transverse_force}. 
As shown in Fig.~\ref{fig:eq_positions} $a_{II}$ decrease the dimer begins to
approximate a single homogenous sphere - at least in terms of location and trap strength. However, for intermediate sized dimers (between $a_{I}/a_{II} = 1.1$ 
to $a_{I}/a_{II}=4$), a second equilibrium position is found below the trapping 
focus. Previous work using the ray-optics model have confirmed even in the case 
that two spheres begin separated the electric field will align the particles as 
such that they make contact and are trapped together about a single trapping 
position \cite{Xu2005}. Furthermore it has been shown through proper manipulation 
of the Gaussian or Bessel beam modes that any number of trapping potentials can 
be developed \cite{Shahabadi2020} for nanoparticles. This result however, is the 
first example of an orientation dependent trapping situation using only a 
$TEM_00$ beam. Typical experimental arrangements cannot determine much information 
on the axial position of a trapped particle relative to the trap focus; this 
result indicates not only that dimers can be trapped in multiple axial positions 
but also their trapping behaviour is heavily dependent on said axial position. 
As such it is necessary that positional information in the z-axis can be elucidated
if multiple spheres are trapped simultaneously.

@@

\subsection{Gyroscopic Precession using asymmetric dimers}
As mentioned in section~\ref{sec:off-axis} for specificity 
sized dimers there is the potential for non-vertical trapping 
orientations in which the dimer is located in a harmonic 
trap. When trapped by a circularly polarised light these 
dimers exhibit gyroscopic precession. As shown in fig~\ref{fig:gyro} 
the dimer's is rotating about it's long axis (as seen by 
the periodic behaviour of $U_x$ and $U_y$), while also precessing 
around the optical axis of the beam, resulting in a second 
order oscillation in $s_z$.
\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{gyroscopic_precession.png}
	\caption{3 second trajectory of a dimer ($a_{I}/a_{II}=2$) trapped in an 
		off axis orientation with a circular polarised beam ($P= 100\ mW$). 
		The far left column depicts the dimer's centre of mass position with 
		time; middle two columns are the $x$, $y$, and $z$ components of the 
		vectors $u_x$ and $u_y$; last column depicts the components of the 
		vector $u_z$ which defines the dimer's orientation.}
	\label{fig:gyro}
\end{figure}

>>>>

\newpage
For completeness the harmonic traps were located for dimers across a range 
of size ratios - from $a_{I}/a_{II} = 1$ to $a_{I}/a_{II}=10$ - while also 
recording the trap stiffness for each trap. The same simulation parameters are 
used here as for figures \ref{fig:paradigmatic} \& \ref{fig:transverse_force}. 
As shown in Fig.~\ref{fig:eq_positions} $a_{II}$ decrease the dimer begins to
approximate a single homogenous sphere - at least in terms of location and trap strength. However, for intermediate sized dimers (between $a_{I}/a_{II} = 1.1$ 
to $a_{I}/a_{II}=4$), a second equilibrium position is found below the trapping 
focus. Previous work using the ray-optics model have confirmed even in the case 
that two spheres begin separated the electric field will align the particles as 
such that they make contact and are trapped together about a single trapping 
position \cite{Xu2005}. Furthermore it has been shown through proper manipulation 
of the Gaussian or Bessel beam modes that any number of trapping potentials can 
be developed \cite{Shahabadi2020} for nanoparticles. This result however, is the 
first example of an orientation dependent trapping situation using only a 
$TEM_00$ beam. Typical experimental arrangements cannot determine much information 
on the axial position of a trapped particle relative to the trap focus; this 
result indicates not only that dimers can be trapped in multiple axial positions 
but also their trapping behaviour is heavily dependent on said axial position. 
As such it is necessary that positional information in the z-axis can be elucidated
if multiple spheres are trapped simultaneously.

@@

\subsection{Gyroscopic Precession using asymmetric dimers}
As mentioned in section~\ref{sec:off-axis} for specificity 
sized dimers there is the potential for non-vertical trapping 
orientations in which the dimer is located in a harmonic 
trap. When trapped by a circularly polarised light these 
dimers exhibit gyroscopic precession. As shown in fig~\ref{fig:gyro} 
the dimer's is rotating about it's long axis (as seen by 
the periodic behaviour of $U_x$ and $U_y$), while also precessing 
around the optical axis of the beam, resulting in a second 
order oscillation in $s_z$.
\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{gyroscopic_precession.png}
	\caption{3 second trajectory of a dimer ($a_{I}/a_{II}=2$) trapped in an 
		off axis orientation with a circuarly polarised beam ($P= 100\ mW$). 
		The far left column depicts the dimer's centre of mass position with 
		time; middle two columns are the $x$, $y$, and $z$ components of the 
		vectors $u_x$ and $u_y$; last column depicts the components of the 
		vector $u_z$ which defines the dimer's orientation.}
	\label{fig:gyro}
\end{figure}
